Exploratory data analysis

### 2019-06-27 analysis/eda.Rmd
add new report

  fv_nri_info.gain5, fv_nri_info.gain10,
  fv_nri_info.gain15, fv_nri_info.gain20,
  fv_nri_info.gain25, fv_nri_info.gain30
)
library("DataExplorer")
library("dplyr")
library("ggsci")
library("ggplot2")
```

>>>>

  fv_nri_info.gain5, fv_nri_info.gain10,
  fv_nri_info.gain15, fv_nri_info.gain20,
  fv_nri_info.gain25, fv_nri_info.gain30
)
library("DataExplorer")
library("dplyr")
library("ggsci")
library("ggplot2")
library("rgdal")
```
